The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-06-24 manuscript/manuscript.tex
Push before John's edit

\begin{document}
\def\lcdm{$\Lambda$CDM}
\def\hst{{\it HST}}
\def\efr{$R_{\mathrm{eff}}$}
\def\galfit{{\sc Galfit}}
\def\mbh{$\mathcal M_{\rm BH}$}
\def\lhost{$L_{\rm host}$}
\def\jcap{Journal of Cosmology and Astroparticle Physics}
\def\halpha{${\it H}\alpha$}
\def\hbeta{${\it H}\beta$}
\def\sersic{S\'ersic}
\def\lenstronomy{{\sc Lenstronomy}}
\def\Reff{{$R_{\mathrm{eff}}$}}
\def\kms{km~s$^{\rm -1}$}
\def\sigstar{{$\sigma_*$}}
\def\smass{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
\newcommand{\sint}{$\sigma_{\rm int}$}
\newcommand{\angstrom}{\text{\normalfont\AA}}
\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}  %For share same footnote
\makeatother

@@

\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{1}, Daeseong Park{7}, Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
 }
 \email{dxh@astro.ucla.edu}
\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
\altaffiltext{4}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
\altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
\altaffiltext{6}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
\altaffiltext{7}{\textcolor{blue}{To be updated}}
\begin{abstract}

The correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties (e.g. stellar mass \smass, luminosity \lhost) suggests an evolutionary connection. A powerful test of this co-evolution hypothesis is to measure the relations \mbh-\lhost\ and \mbh-\smass~(total) at high redshift and compare with the local relation. For this purpose, we obtained multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ emission, we obtained accurate measurements of the host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on near-infrared spectroscopic observations of the broad \halpha~line, which avoids potential uncertainties associated with \Mgii\ or \Civ\ .
%We enlarge the sample using previously published measurements and compare their \mbh-\smass~and \mbh-\lhost~relations to the local to infer their evolution. 
We find that the observed ratio of \mbh/\smass ~is 0.0035, a 0.24~dex offset as compared to the local relation that would lead to a evolution as \mbh/\smass$\propto(1+z)^\gamma$ with $\gamma = 0.80\pm0.30$. However, we expect an offset of 0.21 dex at these redshifts due to a selection bias thus the high-$z$ sample is consistent with the local sample if considering this effect. This is in agreement with the lack of evolution seen in the \mbh/\lhost ~ratios of our sample. Therefore, our results depict a scenario where SMBHs and their host galaxies co-evolve with the possibility for SMBHs to have slightly elevated masses, considering the observed ratios, that may indicate that galaxies with lower angular momentum at high-$z$ may be a bit more efficient to grow their black holes at earlier cosmic times. In any case, the bulge \smass ~mass at a given black hole mass is clearly discrepant with the local relation, since the hosts have a significant amount of stellar mass in a disk, thus leaving the open question as to whether the connection to the bulge is relevant for black hole growth.

@@

\keywords{galaxies: active --- galaxies: evolution}

@@

Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass) and stellar velocity dispersion (\sigstar). These tight correlations may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc). On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering {\color{blue} either the active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or how the growth of these components is connected to the common gas supply~\citep{Cen2015, Menci2016}}.
On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from galaxy assembly (i.e., mergers) which can reproduce the observed correlations.

@@

In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to the highest redshifts where evolutionary effects should be strongest. In particular, we measure the properties of 32 host galaxies in redshift range $1.2<z<1.7$ using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS. Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e. $\sim0.23$ dex,][]{Schulze2014}. The paper is organized as follows. We briefly describe the sample selection and the BH mass of the sample in Section~\ref{sec:data}. We describe the observation and collect the PSF library in Section~\ref{observation}. In Section~\ref{sec:analysis} we decompose our sample and study the host galaxy surface photometry. In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population, which we applied to derive the rest-frame R band \lhost\ and \smass\ and compared to the local samples. Discussion and conclusion are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}. Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$. Magnitudes are given in the AB system.

@@

We construct a sample of broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that meet the following criterion to overcome limitations of previous studies.

@@

\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., H$\alpha$) which avoids potential systematic uncertainties in UV-based estimators \citep{Greene2005}.

@@

\item The large fraction of the sample has addition \hst\ imaging (i.e., \hst/ACS, providing extra color information to achieve reliable K-corrections and stellar mass determinations. 
\end{itemize}

\subsection{Target selection}\label{sec:target_selection}

@@

\begin{deluxetable*}{llccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Details of Observation} 
\tablehead{ 
\colhead{Object ID} &
\colhead{$z$} & 
\colhead{WFC3/Filter} &
\colhead{$RA$}&
\colhead{$DEC$}&
\colhead{Observing date}&
\colhead{Exposure time (s)}
\\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
\enddata
\label{tab:objlist}
\tablecomments{
Column 1: Object field and ID.
Column 2: Redshifts.
Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
Column 6: The observing start date.
}
\end{deluxetable*}

\subsection{Details on BH mass estimates}
\label{mbh}
The \mbh\ of type-1 AGNs can be inferred using the so-called virial method~\citep{Peterson2004, Shen2013}. The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas. In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. As a result, the estimation of the \mbh\ is achieved by these measurements.

@@

Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. {\color{blue} 3/32 systems, including CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}.
14/32 systems have both \halpha\ and \hbeta\ emission line information. However, we only adopt the value for \mbh\ using the \halpha\ emission line, to assure they are self-consistent.
%Given that 18/32 sample are lack of \hbeta\ line, we thus adopt the \mbh\ estimated by \halpha\ to our sample in the rest of the work, to avoid the scatter of the \mbh\ by \hbeta\ unevenly spreading into the overall sample.

We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}. 
}

>>>>

\begin{document}
\def\lcdm{$\Lambda$CDM}
\def\hst{{\it HST}}
\def\efr{$R_{\mathrm{eff}}$}
\def\galfit{{\sc Galfit}}
\def\mbh{$\mathcal M_{\rm BH}$}
\def\lhost{$L_{\rm host}$}
\def\jcap{Journal of Cosmology and Astroparticle Physics}
\def\halpha{${\rm H}\alpha$}
\def\hbeta{${\rm H}\beta$}
\def\sersic{S\'ersic}
\def\lenstronomy{{\sc Lenstronomy}}
\def\Reff{{$R_{\mathrm{eff}}$}}
\def\kms{km~s$^{\rm -1}$}
\def\sigstar{{$\sigma_*$}}
\def\smass{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
\newcommand{\sint}{$\sigma_{\rm int}$}
\newcommand{\angstrom}{\text{\normalfont\AA}}
\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}  %For share same footnote
\makeatother

@@

\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{4}, Malte Schramm\altaffilmark{4}, Simon Birrer\altaffilmark{1}, Daeseong Park\altaffilmark{5}, Knud Jahnke\altaffilmark{6}, {\color{blue} Federica Duras\altaffilmark{7, 8}, Angela Bongiorno\altaffilmark{8}}
 }
 \email{dxh@astro.ucla.edu}
\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{3}{{\color{blue} Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}}
\altaffiltext{4}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
\altaffiltext{5}{Korea Astronomy and Space Science Institute, Deajeon, 34055, Republic of Korea}
\altaffiltext{6}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117, Heidelberg, Germany}
\altaffiltext{7}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
\altaffiltext{8}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
\begin{abstract}

The correlations between the mass of a supermassive black hole (SMBH) and its host galaxy properties (e.g. stellar mass \smass, luminosity \lhost) suggests an evolutionary connection. A powerful test of this co-evolution hypothesis is to measure the relations \mbh-\lhost\ and \mbh-\smass~(total) at high redshift and compare with the local relation. For this purpose, we obtained multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ emission, we obtained accurate measurements of the host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on near-infrared spectroscopic observations of the broad \halpha~line, which avoids potential uncertainties associated with \Mgii\ or \Civ\ .
%We find that the observed ratio of \mbh/\smass ~is 0.0035, a 0.24~dex offset as compared to the local relation that would lead to a evolution as \mbh/\smass$\propto(1+z)^\gamma$ with $\gamma = 0.80\pm0.30$. However, we expect an offset of 0.21 dex at these redshifts due to a selection bias thus the high-$z$ sample is consistent with the local sample if considering this effect. This is in agreement with the lack of evolution seen in the \mbh/\lhost ~ratios of our sample. Therefore, our results depict a scenario where SMBHs and their host galaxies co-evolve with the possibility for SMBHs to have slightly elevated masses, considering the observed ratios, that may indicate that galaxies with lower angular momentum at high-$z$ may be a bit more efficient to grow their black holes at earlier cosmic times. In any case, the bulge \smass ~mass at a given black hole mass is clearly discrepant with the local relation, since the hosts have a significant amount of stellar mass in a disk, thus leaving the open question as to whether the connection to the bulge is relevant for black hole growth.
{\color{blue}
We find that the observed ratio of \mbh/\smass is larger at $z\sim1.7$ than the one in the local universe. However, when accounting for the selection effect (using two independent methods), we find that the high redshift points can be consistent with the local relation, assuming the scatter is unchanged or larger. The relationship between \mbh\ and host galaxy total luminosity paints a similar picture: the ratio is larger than the local universe, but given the uncertainties and selection effects one cannot conclude that the offset is significant. Therefore, given the uncertainties, our results are consistent with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former is somewhat anticipated. Considering that the local relationships general apply to bulges, and our hosts have a significant amount of stellar mass in a disk, observations are consistent with a scenario in which stellar mass and luminosity is transferred from the angular momentum supported to the pressure supported component of the galaxy by secular processes or minor mergers at a faster rate than that of mass accretion onto the SMBH.
}

@@

\keywords{galaxies: active -- galaxies: evolution}

@@

Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass) and stellar velocity dispersion (\sigstar). These tight correlations (known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc). On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering {\color{blue} either the active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or how the growth of these components is connected to the common gas supply~\citep{Cen2015, Menci2016}}.
On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from galaxy assembly (i.e., mergers) which can reproduce the observed correlations.

@@

In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to the highest redshifts where evolutionary effects should be strongest. In particular, we measure the properties of 32 host galaxies in redshift range $1.2<z<1.7$ using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS. Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e. $\sim0.23$ dex,][]{Schulze2014}.

The paper is organized as follows. We briefly describe the sample selection and the BH mass of the sample in Section~\ref{sec:data}. We describe the observation and collect the PSF library in Section~\ref{observation}. In Section~\ref{sec:analysis} we decompose our sample and study the host galaxy surface photometry. In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population, which we applied to derive the rest-frame R band \lhost\ and \smass\ and compared to the local samples. Discussion and conclusion are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}. Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$. Magnitudes are given in the AB system.

@@

We construct a sample of broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that meet the following criteria to overcome limitations of previous studies:

@@

\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., \halpha) which avoids potential systematic uncertainties in UV-based estimators \citep{Greene2005}.

@@

\item The large fraction of the sample has addition \hst\ imaging (i.e., \hst/ACS), providing extra color information to achieve reliable K-corrections and stellar mass determinations. 
\end{itemize}

\subsection{Sample selection}\label{sec:target_selection}

@@

\begin{deluxetable*}{llccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Details of Observation} 
\tablehead{ 
\colhead{Object ID} &
\colhead{$z$} & 
\colhead{WFC3/Filter} &
\colhead{$RA$}&
\colhead{$DEC$}&
\colhead{Observing date}&
\colhead{Exposure time (s)}
\\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
\enddata
\label{tab:objlist}
\tablecomments{
Column 1: Object field and ID.
Column 2: Redshifts.
Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
Column 6: The observing start date.
Column 7: Total exposure time.
}
\end{deluxetable*}

\subsection{Expected bias from the selection function}

\label{sec:sf_framework}

Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios. It is well known that sample selection effects must be taken into account in order to  interpret the observed black hole-host relations and measure its evolution with redshift avoiding bias ~\citep{Schulze2011, Tre++07, Bennert++2011, Park15}. The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (like AGN luminosity and line strength and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors.

Correcting for observational biases requires a well-characterized selection function, such as the one we have for our sample, and a model of the black hole mass function, and the evolution of the correlations between \mbh, and other properties.

In order to get a sense for the amount of bias that we can anticipate given our selection function, we use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias. In this framework, under the assumption of no evolution of the correlations between \mbh\ and host-galaxy properties, one can compute the expected bias for a given sample, prior to observations. The key ingredient of this model are the local \mbh\ host-galaxy property correlations, the black hole mass function and Eddington ratio distribution at the redshift of observation. The latter two quantities are estimated from the type-1 AGN distributions corrected to represent the parent population of all SMBH hosts, including the inactive ones.

Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model. {\bf TT: we should say something about the uncertainty here for example the following.} This bias correction should be considered an approximate estimate, with an uncertainty that depends on the uncertainty of the inputs. Furthermore, if the scaling relations actually evolve, one needs to introduce a model for the evolution in order to infer the underlying bias-corrected trends. We will revisit these issues in Section~\ref{select_eff}.

\subsection{Details on BH mass estimates}
\label{mbh}
The \mbh\ of type-1 AGNs can be inferred using the so-called virial method~\citep{Peterson2004, Shen2013}. The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas. Under these assumptions, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. As a result, the estimation of the \mbh\ is achieved by these measurements.

@@

Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. There are 3/32 systems (i.e. CDFS-1, CDFS-229 and CDFS-724) not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}.
14/32 systems have both \halpha\ and \hbeta\ emission line information. However, we only adopt the value for \mbh\ using the \halpha\ emission line, to assure they are self-consistent.

We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}.
